Population structure and phenotypic variation of \emph{Sclerotinia sclerotiorum} from dry bean (\emph{Phaseolus vulgaris}) in the United States

### 2017-11-10 doc/manuscript/manuscript.tex
add current results
update manuscript with SE comments

Currently, there are no commercially available resistant cultivars of
dry bean (Otto-Hanson et al., 2011). Organized breeding efforts have
used a common-garden approach with white mold screening nurseries in dry
bean production areas across the United States with additional sites in
Australia, France, and Mexico (Steadman et al., 2003, 2004, 2005, 2006;
Otto-Hanson \& Steadman, 2007, 2008; McCoy \& Steadman, 2009). These
white mold screening nurseries use no chemical or cultural treatments
against \emph{S. sclerotiorum} and employ standardized protocols for
screening new cultivars for resistance to white mold (Steadman et al.,
2003; Otto-Hanson et al., 2011). These protocols included three
established cultivars used for comparison in the trials: Beryl (great
northern bean, susceptible), Bunsi (aka Ex Rico, navy bean, low
susceptibility), and G122 (cranberry bean, partial resistance) (Tu \&
Beversdorf, 1982; Steadman et al., 2005; Otto-Hanson et al., 2011). It
has previously been shown that aggressiveness (the severity of disease
symptoms on the host) is significantly different across white mold
screening nursery sites in separate geographic regions (Otto-Hanson et
al., 2011). The genetic structure and mode of reproduction in these
populations, however, is currently unknown.

@@

Nearly all population genetic studies of \emph{S. sclerotiorum} employ a
macroscopic assay to determine mycelial compatibility, the ability for
fungal hyphae from different colonies to appear to grow together without
forming a barrier of dead cells between them (known as a barrage line,
Fig. \ref{mcg-fig}B) (Leslie, 1993; Sirjusingh \& Kohn, 2001). Mycelial
compatibility has been used as a proxy for vegetative compatibility, a
fungal trait controlled by several independent genes controlling the
ability for two hyphae to fuse and grow as a single unit (Fig.
\ref{mcg-fig}A) (Leslie, 1993; Schafer \& Kohn, 2006). Because of the
genetic connection to vegetative compatibility, two isolates that are
mycelially compatible were considered clones (Leslie, 1993); but
correlation with genetic markers, such as microsatellites, have shown
mixed results (Ford et al., 1995; Micali \& Smith, 2003; Jo et al.,
2008; Attanayake et al., 2012; Papaioannou \& Typas, 2014; Lehner et
al., 2017). However, a question remains about the relationship between
mycelial compatibility groups and clonal genotypes.

@@

We used ANOVA to assess if aggressiveness (determined via straw test on
a scale of 1--9) was significantly different with respect to Region,
MCG, or multilocus haplotype (MLH). To minimize complications due to
small sample sizes, we chose the top 10 MCGs, representing 56.5\% of the
isolates collected, the 10 most abundant MLHs representing 26.7\% of the
isolates, and populations with more than five isolates. If ANOVA results
were significantly different at \(\alpha\) = 0.05, pairwise differences
were assessed using Tukey's HSD test (\(\alpha\) = 0.05) using the
\texttt{HSD.test()} function in the package \emph{agricolae} version
1.2.8 (Mendiburu \& Simon, 2015).

@@

A total of 366 isolates were collected from 2003 to 2012 (except 2006
and 2011) from diseased dry bean plants in 11 states in the United
States as well as Australia, France, and Mexico (Table
\ref{tab:isolate-table}). With the 11 loci used in the analyses (Table
\ref{tab:locus-stats}), we observed a total of 165 MLHs (215 with 16
loci). These 11 loci represented 7 chromosomes in the \emph{S.
sclerotiorum} genome with a minimum distance of 55Kbp between two loci
on the same chromosome. Over 50\% of the isolates came from four states,
MI (62), ND (60), WA (59), NE (47). Four regions had fewer than 10
isolates, Australia (6), WI (2), NY (1), ID (1). We observed 87 MCGs,
the most abundant of which (`MCG 5') was represented by 73 isolates over
37 MLHs (Fig \ref{biggraph}A,C).

@@

After clone-correction on the hierarchy of Region/Source/Host/Year, a
total of 48 isolates were removed from the data set, resulting in 318
isolates representing 165 MLHs that were used in subsequent analyses
(Table \ref{tab:iatab}). The results showed that, in terms of genotypic
diversity (\emph{H}, \emph{G}, and \(\lambda\)), WA was the most diverse
population with both \emph{G} (54.3) and \(e^H\) (55.3) being close to
the observed number of MLGs (56). This indicated that there are few
duplicated genotypes in WA (Table \ref{tab:iatab}). A more useful metric
to compare populations, however, is \(E_5\), which scales from 0 to 1
where 1 indicates all unique genotypes (Grünwald et al., 2003).
Evaluating by \(E_5\) shows that both MI and NE exhibit lower than
average values, indicating that there are over-represented genotypes in
the popualtions (table \ref{tab:iatab}). When we look at Mexico, we can
observed that it had relatively high values of \(E_5\) and genotypic
diversity, but low richness, as measured by \emph{eMLG}. Moreover,
Mexico had the lowest value for \emph{h}, which is a measure of allelic
diversity. Nearly all populations showed evidence for linkage (Table
\ref{tab:iatab}), which serves as evidence for clonal reproduction or
other forms of non-random mating. The only exceptions are CA (\emph{P} =
0.043) and Australia (\emph{P} = 0.052). Both of these populations
showed only moderate significance with \(\bar{r}_d\) values of 0.03 and
0.12, respectively.

@@

\begin{longtable}[]{@{}clrllc@{}}
\caption{\label{tab:amova} Comparison of populations in the white mold
screening nurseries (wmn) and producer fields using an analysis of
molecular variance on Bruvo's genetic distance showing no apparent
differentiation between wmn and other sources. The hierarchy was
constructed as Source/Region where source is defined as belonging to a
wmn or producer field. Bold \(\Phi\) values indicate significant
difference (\emph{P} \textless{} 0.05). S.S. = Sum of Squares, d.f. =
degrees of freedom.}\tabularnewline
\toprule
\begin{minipage}[b]{0.32\columnwidth}\centering\strut
Hierarchy\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedright\strut
d.f.\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\raggedleft\strut
S.S.\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\raggedright\strut
\% variation\strut
\end{minipage} & \begin{minipage}[b]{0.19\columnwidth}\raggedright\strut
\(\Phi\) statistic\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\centering\strut
\emph{P}\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.32\columnwidth}\centering\strut
Hierarchy\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedright\strut
d.f.\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\raggedleft\strut
S.S.\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\raggedright\strut
\% variation\strut
\end{minipage} & \begin{minipage}[b]{0.19\columnwidth}\raggedright\strut
\(\Phi\) statistic\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\centering\strut
\emph{P}\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.32\columnwidth}\centering\strut
Between Region\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright\strut
13\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedleft\strut
10.19\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedright\strut
8.45\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedright\strut
\textbf{0.0845}\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering\strut
0.033\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.32\columnwidth}\centering\strut
Between Source within Region\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright\strut
8\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedleft\strut
2.74\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedright\strut
-2.29\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedright\strut
-0.0250\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering\strut
0.448\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.32\columnwidth}\centering\strut
Between Year within Source\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright\strut
22\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedleft\strut
9.37\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedright\strut
16.28\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedright\strut
\textbf{0.173}\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering\strut
0.001\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.32\columnwidth}\centering\strut
Within Year\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright\strut
274\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedleft\strut
47.30\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedright\strut
77.56\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedright\strut
\textbf{0.224}\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering\strut
0.001\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

With the exception of the WA Region, populations that were sampled
across several years appeared to be relatively stable over time with
overlapping distributions in the DAPC (i.e.~NE and MI, Fig.
\ref{DAPC-RY}). DAPC is based on the principal components of allele
counts (Jombart et al., 2010). Unlike Bruvo's distance, this does not
take into account the magnitude of the difference between alleles, which
could inflate the distance measure in the presence of private alleles
(Bruvo et al., 2004). While we found no evidence of private alleles in
the Mexico and CA isolates, we did find that the alleles driving the
first axis in figure \ref{DAPC}A (alleles 174, 256, and 372 in loci 7-2,
8-3, and 9-2, respectively) were overrepresented in Mexico (where
\textgreater{}75\% of the alleles came from the region). However, all
three of these alleles i) conform to the expected stepwise mutation
model (Bruvo et al., 2004) and ii) are at or near the extremes of the
total range (except for allele 372 at locus 9-2). Moreover, the fact
that we find three alleles at three independent loci segregating for
Mexico suggests that the pattern separating these populations from the
others was not an artifact. We believe that the differences we observe
from Mexico may reflect differences in climate.

@@

One of the main limitations of this study is the focus on \emph{P.
vulgaris} as a host. It has been shown that \emph{S. sclerotiorum} in
the midwestern United States does not have a particular preference for
host (Aldrich-Wolfe et al., 2015). If the distribution of \emph{S.
sclerotiorum} is even across agricultural hosts in the USA, then our
sample may yet be representative of the genetic pool present in other
crops and weedy species. Additionally, while we found no signficant
association between genotype and aggressiveness, it is important to note
that the straw test is only one measure of aggressiveness. Additional
phenotypes for aggressiveness should be evaluated for future studieds.

@@

\hypertarget{ref-knodel2012dry}{}
Knodel, J., Beauzay, P., Franzen, D., Kandel, H., Markell, S., Osorno,
J., Pasche, J., \& Zollinger, R. (2012). 2012 dry bean grower survey of
production, pest problems and pesticide use in Minnesota and North
Dakota. \emph{North Dakota State University Extension}.

\hypertarget{ref-knodel2015dry}{}
Knodel, J., Beauzay, P., Franzen, D., Kandel, H., Markell, S., Osorno,
J., Pasche, J., \& Zollinger, R. (2015). 2015 dry bean grower survey of
production, pest problems and pesticide use in Minnesota and North
Dakota. \emph{North Dakota State University Extension}.

\hypertarget{ref-knodel2016dry}{}
Knodel, J., Beauzay, P., Franzen, D., Kandel, H., Markell, S., Osorno,
J., Pasche, J., \& Zollinger, R. (2016). 2016 dry bean grower survey of
production, pest problems and pesticide use in Minnesota and North
Dakota. \emph{North Dakota State University Extension}.

@@

\hypertarget{ref-ramasubramaniam2008estimates}{}
Ramasubramaniam, H., Río Mendoza, L. E. del, \& Bradley, C. A. (2008).
Estimates of yield and economic losses associated with white mold of
rain-fed dry bean in north dakota. \emph{Agronomy Journal},
\emph{100}(2), 315. \url{https://doi.org/10.2134/agronj2007.0127}

@@

\hypertarget{ref-strausbaugh2003management}{}
Strausbaugh, C., \& Forster, R. (2003). Management of white mold of
beans. \emph{Pacific Northwest Extension}. Retrieved from
\url{http://http://www.extension.uidaho.edu/publishing/pdf/PNW/PNW0568.pdf}

@@

\hypertarget{ref-tu1982tolerance}{}
Tu, J. C., \& Beversdorf, W. D. (1982). Tolerance to white mold
(\emph{Sclerotinia sclerotiorum} (lib.) de bary) in Ex Rico 23, a
cultivar of white bean (\emph{Phaseolus vulgaris} l.). \emph{Canadian
Journal of Plant Science}, \emph{62}(1), 65--69.
\url{https://doi.org/10.4141/cjps82-010}

>>>>

Currently, there are no commercially available resistant cultivars of
dry bean (Otto-Hanson et al., 2011). Organized breeding efforts have
used a common-garden approach with white mold screening nurseries in dry
bean production areas across the United States with additional sites in
Australia, France, and Mexico (Steadman et al., 2003, 2004, 2005, 2006;
Otto-Hanson \& Steadman, 2007, 2008; McCoy \& Steadman, 2009). These
white mold screening nurseries use no chemical or cultural treatments
against \emph{S. sclerotiorum} and employ standardized protocols for
screening new cultivars for resistance to white mold (Steadman et al.,
2003; Otto-Hanson et al., 2011). These protocols included three
established cultivars used for comparison in the trials: Beryl (great
northern bean, susceptible), Bunsi (a.k.a. Ex Rico, navy bean, low
susceptibility), and G122 (cranberry bean, partial resistance) (Tu \&
Beversdorf, 1982; Steadman et al., 2005; Otto-Hanson et al., 2011). It
was previously shown that aggressiveness (the severity of disease
symptoms on the host) is significantly different across white mold
screening nursery sites in separate geographic regions (Otto-Hanson et
al., 2011). The genetic structure and mode of reproduction in these
populations, however, is currently unknown.

@@

Nearly all population genetic studies of \emph{S. sclerotiorum} employ a
macroscopic assay to determine mycelial compatibility, the ability for
fungal hyphae from different colonies to appear to grow together without
forming a barrier of dead cells between them (known as a barrage line,
Fig. \ref{mcg-fig}B) (Leslie, 1993; Sirjusingh \& Kohn, 2001). Mycelial
compatibility has been used as a proxy for vegetative compatibility, a
fungal trait controlled by several independent genes controlling the
ability for two hyphae to fuse and grow as a single unit (Fig.
\ref{mcg-fig}A) (Leslie, 1993; Schafer \& Kohn, 2006). Because of the
genetic connection to vegetative compatibility, two isolates that are
mycelially compatible were considered clones (Leslie, 1993); but
correlation with genetic markers, such as microsatellites, have shown
mixed results (Ford et al., 1995; Micali \& Smith, 2003; Jo et al.,
2008; Attanayake et al., 2012; Papaioannou \& Typas, 2014; Lehner et
al., 2017). Thus, the relationship between mycelial compatibility groups
and clonal genotypes remains unclear.

@@

We used ANOVA to assess if aggressiveness (determined via straw test on
a scale of 1--9 as described above) was significantly different with
respect to Region, MCG, or multilocus haplotype (MLH). To minimize
complications due to small sample sizes, we chose the top 10 MCGs,
representing 56.5\% of the isolates collected, the 10 most abundant MLHs
representing 26.7\% of the isolates, and populations with more than five
isolates. If ANOVA results were significantly different at \(\alpha\) =
0.05, pairwise differences were assessed using Tukey's HSD test
(\(\alpha\) = 0.05) using the \texttt{HSD.test()} function in the
package \emph{agricolae} version 1.2.8 (Mendiburu \& Simon, 2015).

@@

A total of 366 isolates were collected from 2003 to 2012 (except 2006
and 2011) from diseased dry bean plants in 11 states in the United
States as well as Australia, France, and Mexico (Table
\ref{tab:isolate-table}). With the 11 loci used in the analyses (Table
\ref{tab:locus-stats}), we observed a total of 165 MLHs (215 with 16
loci). These 11 loci are found on 7 chromosomes in the \emph{S.
sclerotiorum} genome with a minimum distance of 55Kbp between two loci
on the same chromosome. Over 50\% of the isolates came from four states,
MI (62), ND (60), WA (59), NE (47). Four regions had fewer than 10
isolates, Australia (6), WI (2), NY (1), ID (1). We observed 87 MCGs,
the most abundant of which (`MCG 5') was represented by 73 isolates over
37 MLHs (Fig \ref{biggraph}A,C).

@@

After clone-correction on the hierarchy of Region/Source/Host/Year, a
total of 48 isolates were removed from the data set, resulting in 318
isolates representing 165 MLHs that were used in subsequent analyses
(Table \ref{tab:iatab}). The results showed that, in terms of genotypic
diversity (\emph{H}, \emph{G}, and \(\lambda\)), WA was the most diverse
population with both \emph{G} (54.3) and \(e^H\) (55.3) being close to
the observed number of MLGs (56). This indicated that there are few
duplicated genotypes in WA (Table \ref{tab:iatab}). A more useful metric
to compare populations, however, is \(E_5\), which scales from 0 to 1,
where 1 indicates all unique genotypes (Grünwald et al., 2003).
Evaluating by \(E_5\) shows that both MI and NE exhibit lower than
average values, indicating that there are over-represented genotypes in
the popualtions (table \ref{tab:iatab}). When we look at Mexico, we
observed that it had relatively high values of \(E_5\) and genotypic
diversity, but low richness, as measured by \emph{eMLG}. Moreover,
Mexico had the lowest value for \emph{h}, which is a measure of allelic
diversity. Nearly all populations showed evidence for linkage (Table
\ref{tab:iatab}), which serves as evidence for clonal reproduction or
other forms of non-random mating. The only exceptions are CA (\emph{P} =
0.043) and Australia (\emph{P} = 0.052). Both of these populations
showed only moderate significance with \(\bar{r}_d\) values of 0.03 and
0.12, respectively.

@@

\begin{longtable}[]{@{}clrllc@{}}
\caption{\label{tab:amova} Comparison of populations in the white mold
screening nurseries (wmn) and producer fields using an analysis of
molecular variance on Bruvo's genetic distance showing no apparent
differentiation between wmn and other sources. The hierarchy was
constructed as Source/Region where source is defined as belonging to a
wmn or producer field. Bold \(\Phi\) values indicate significant
difference (\emph{P} \textless{} 0.05). S.S. = Sum of Squares, d.f. =
degrees of freedom.}\tabularnewline
\toprule
\begin{minipage}[b]{0.32\columnwidth}\centering\strut
Hierarchy\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedright\strut
d.f.\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\raggedleft\strut
S.S.\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\raggedright\strut
\% variation\strut
\end{minipage} & \begin{minipage}[b]{0.19\columnwidth}\raggedright\strut
\(\Phi\) statistic\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\centering\strut
\emph{P}\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.32\columnwidth}\centering\strut
Hierarchy\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedright\strut
d.f.\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\raggedleft\strut
S.S.\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\raggedright\strut
\% variation\strut
\end{minipage} & \begin{minipage}[b]{0.19\columnwidth}\raggedright\strut
\(\Phi\) statistic\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\centering\strut
\emph{P}\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.32\columnwidth}\centering\strut
Between Region\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright\strut
13\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedleft\strut
10.19\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedright\strut
8.45\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedright\strut
\textbf{0.0845}\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering\strut
0.031\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.32\columnwidth}\centering\strut
Between Source within Region\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright\strut
8\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedleft\strut
2.74\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedright\strut
-2.29\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedright\strut
-0.0250\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering\strut
0.497\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.32\columnwidth}\centering\strut
Between Year within Source\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright\strut
22\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedleft\strut
9.37\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedright\strut
16.28\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedright\strut
\textbf{0.173}\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering\strut
0.001\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.32\columnwidth}\centering\strut
Within Year\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright\strut
274\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedleft\strut
47.30\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedright\strut
77.56\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedright\strut
\textbf{0.224}\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering\strut
0.001\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

With the exception of the WA Region, populations that were sampled
across several years appeared to be relatively stable over time with
overlapping distributions in the DAPC (i.e.~NE and MI, Fig.
\ref{DAPC-RY}). DAPC is based on the principal components of allele
counts (Jombart et al., 2010). Unlike Bruvo's distance, this does not
take into account the magnitude of the difference between alleles, which
could inflate the distance measure in the presence of private alleles
(Bruvo et al., 2004). While we found no evidence of private alleles in
the Mexico and CA isolates, we did find that the alleles driving the
first axis in figure \ref{DAPC}A (alleles 174, 256, and 372 in loci 7-2,
8-3, and 9-2, respectively) were overrepresented in Mexico (where
\textgreater{}75\% of the alleles came from the region). However, all
three of these alleles, i) conform to the expected stepwise mutation
model (Bruvo et al., 2004) and ii) are at or near the extremes of the
total range (except for allele 372 at locus 9-2). Moreover, the fact
that we find three alleles at three independent loci segregating for
Mexico suggests that the pattern separating these populations from the
others was not an artifact. We believe that the differences in
populations observed from Mexico may be due to differences in climate
that allow greater diversification via sexual outcrossing.

@@

One of the main limitations of this study is the focus on \emph{P.
vulgaris} as a host. It has been shown that \emph{S. sclerotiorum} in
the midwestern United States does not have a particular preference for
host (Aldrich-Wolfe et al., 2015). If the distribution of \emph{S.
sclerotiorum} is even across agricultural hosts in the USA, then our
sample may yet be representative of the genetic pool present in other
crops and weedy species. Additionally, while we found no signficant
association between genotype and aggressiveness, it is important to note
that the straw test is only one measure of aggressiveness. Additional
phenotypes for aggressiveness should be evaluated for future studies.

@@

\hypertarget{ref-knodel2012dry}{}
Knodel, J., Beauzay, P., Franzen, D., Kandel, H., Markell, S., Osorno,
J., Pasche, J., \& Zollinger, R. (2012). 2012 dry bean grower survey of
production, pest problems and pesticide use in Minnesota and North
Dakota. \emph{North Dakota State University Extension}, \emph{E1640}.

\hypertarget{ref-knodel2015dry}{}
Knodel, J., Beauzay, P., Franzen, D., Kandel, H., Markell, S., Osorno,
J., Pasche, J., \& Zollinger, R. (2015). 2015 dry bean grower survey of
production, pest problems and pesticide use in Minnesota and North
Dakota. \emph{North Dakota State University Extension}, \emph{E1802}.

\hypertarget{ref-knodel2016dry}{}
Knodel, J., Beauzay, P., Franzen, D., Kandel, H., Markell, S., Osorno,
J., Pasche, J., \& Zollinger, R. (2016). 2016 dry bean grower survey of
production, pest problems and pesticide use in Minnesota and North
Dakota. \emph{North Dakota State University Extension}, \emph{E1841}.

@@

\hypertarget{ref-ramasubramaniam2008estimates}{}
Ramasubramaniam, H., del Río Mendoza, L. E., \& Bradley, C. A. (2008).
Estimates of yield and economic losses associated with white mold of
rain-fed dry bean in North Dakota. \emph{Agronomy Journal},
\emph{100}(2), 315. \url{https://doi.org/10.2134/agronj2007.0127}

@@

\hypertarget{ref-strausbaugh2003management}{}
Strausbaugh, C., \& Forster, R. (2003). Management of white mold of
beans. \emph{Pacific Northwest Extension}, \emph{PNW568}. Retrieved from
\url{http://http://www.extension.uidaho.edu/publishing/pdf/PNW/PNW0568.pdf}

@@

\hypertarget{ref-tu1982tolerance}{}
Tu, J. C., \& Beversdorf, W. D. (1982). Tolerance to white mold
(\emph{Sclerotinia sclerotiorum} (Lib.) De Bary) in Ex Rico 23, a
cultivar of white bean (\emph{Phaseolus vulgaris} L.). \emph{Canadian
Journal of Plant Science}, \emph{62}(1), 65--69.
\url{https://doi.org/10.4141/cjps82-010}
